Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-09-01 paper.tex
Cite Self-driving paper for digital twins

\section{Introduction}
The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution. As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value. This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems. Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models. We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
\begin{enumerate}
  \item Data owners do not have much control over their data and their data are locked in silos managed by products and services companies.
  \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
  \item Data owners do not know how to discover knowledge from raw data.
\end{enumerate}

>>>>

\section{Introduction}
The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution. As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value. This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems. Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models. We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
\begin{enumerate}
  \item Data owners do not have much control over their data and their data are locked in silos managed by products and services companies.
  \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
  \item Data owners do not know how to discover knowledge from raw data.
\end{enumerate}
